The Chemistry Development Kit (CDK): atom typing, rendering, molecular formulas, and substructure searching

### 2016-10-09 article.tex
simpler file name
More consistent with the text after the code example

\vspace{0.2cm}
\begin{verbatim}
new DepictionGenerator()
  .withSize(300, 300)
  .depict(benzene)
  .writeTo("BenzeneLocalized.png");
\end{verbatim}
\vspace{0.2cm}

@@

  The structure diagram layout has been rewritten and the new code solves a
  number of long standing issues. In particular, collision detection has been
  greatly improved. Figure~\ref{fig:sdg} shows a difference in output
  between  
  the old code base, with and without overlap resolving, and with the
  new code. The latest implementation simplifies the generation of 2D
  coordinates as shown below:

>>>>

\vspace{0.2cm}
\begin{verbatim}
new DepictionGenerator()
  .withSize(300, 300)
  .depict(benzene)
  .writeTo("benzene.png");
\end{verbatim}
\vspace{0.2cm}

@@

  The structure diagram layout has been rewritten and the new code solves a
  number of long standing issues. In particular, collision detection has been
  greatly improved. Figure~\ref{fig:sdg} shows a difference in output
  between  
  the old code base, with and without overlap resolving, and with the
  new code. Generation of 2D coordinates is done as shown below:
